Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-11-03 Cost_manuscript.Rmd
restructuring modeling approach

  We begun the modeling approach by fitting a fixed subjective OC for each type of demand (see Operationalization of Cost), which acted as a base model. OC was computed as the product of a free parameter (gamma) and the handling time. Gamma can be interpreted as the subjective value of each second spent in an environment. If a trial's reward rate (i.e. offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives. In other words, individuals with higher gammas required higher rewards in order to accept a given offer. We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type

@@

  The adaptive nature of choices in this experiment demanded more flexibility than the single-parameter model fitted above. Based on the results across experiments, an adequate model of behavior should meet X criteria: 1) show deviations from optimality that were not simply due to overharvesting 2) persistently higher acceptances for cognitive effort when faced with single behavioral costs; 3) slight reduction of acceptances in effortful conditions (**fatigue?**); 4) an initial preference for cognitive effort trials when foraging for costs and rewards 5) this preference disappears as acceptances decreased to a common rate across costs; 6) participants kept track of recent offer history; 7) effects were robust to block order effects. Alternative foraging models from the literature were not fitted, as they did not qualitatively meet these criteria (wikenheiser, C&D, Fawcett...)

>>>>

  We performed model comparisons to identify qualities that transcended both experiments. An adequate model should meet seven criteria derived from the observed choice behavior: 1) show deviations from optimality that were not simply due to overharvesting 2) keep track of recent offer history; 3) experience a slight reduction of acceptances in effortful conditions; 4) persistently display higher acceptances for cognitive effort when faced with single behavioral costs; 4) initially match this preference for cognitive effort trials when foraging for demands and rewards; 5) display a disappearance of this preference as acceptances decreased to a common rate across costs; and 7) not be affected by block order effects. These conditions discarded a number of popular explanatory candidates, including.... (wikenheiser, C&D, Fawcett...). We therefore did not include these models into our comparison.

  We started by fitting a base model, in which a subjective OC was fit for each type of demand (see Operationalization of Cost). OC was computed as the product of a free parameter (gamma) and the handling time. Gamma can be interpreted as the subjective value of each second spent in an environment. If a trial's reward rate (i.e. offer amount divided by the handling time) fell below gamma, a participant was better off finding more profitable alternatives. In other words, individuals with higher gammas required higher rewards in order to accept a given offer. We used a softmax function to model each participant’s probability of completing a trial based on the difference between the delayed reward’s magnitude and the estimated OC for each cost type

@@
